Stochastic Variance Reduced Policy Gradient

### 2018-01-22 svrpg.tex
Added Stopping condition section

@@

We decide to use the following models of Rllab: \emph{Cart-Pole Balancing} ,\emph{Mujoco Swimmer},\emph{Mujoco Half Cheetah}.

In all the experiments we face with GPOMDP standard algorithm. GPOMDP uses a number of trajectories per batch that is equal to the number of trajectories used in SVRPG mini-batch size.
The neural network and the learning rate are the same for GPOMDP and SVRPG.
In SVRPG we implemented two different Adam parameters: the first one for Snapshot and the second one for sub-iterations.
The stopping condition depends on the maximum number of sub-iterations and on the step size of sub-iteration: in particular we stop if the ratio of step size to number of trajectories used results smaller in sub-iteration than in snapshot.
We fixed the maximum number of trajectories that both the algorithms can use.

>>>>

\section{Stopping Condition}\label{sec:stopping}
In practice ,the performance of the SVRPG algorithm is sensitive to the number of sub-iterations.
As the number of sub-iterations increases, the variance of the importance weights and the gradient increases too.
Therefore, the SVRPG algorithm fails in its primary aim of stabilizing the gradient estimate.
A fixed number of sub-iterations is not the optimal choice.
Few sub-iterations lead to few updates, many update lead to increases of variance.

We introduce two stopping condition: maximum number of sub-iterations and learning rate of Adam sub-iterations.
Adam update rule help to stabilize the gradient estimate. In fact, this method computes adaptive learning rates for each parameter that depends by history of gradients' variance.
In particular we use different Adam parameters: the first one for snapshot update and the second one for the sub-iterations update.
We stop if:

\[\frac{\alpha_{snap}}{N}>\frac{\alpha_{sub-iter}}{M}\]

where M is the sub-iterations batch size.

@@

We decide to use the following models of Rllab: \emph{Cart-Pole Balancing}, \emph{Mujoco Swimmer}, \emph{Mujoco Half Cheetah}.

In all the experiments we face with GPOMDP standard algorithm. GPOMDP uses a number of trajectories per batch that is equal to the number of trajectories used in SVRPG mini-batch size.
The neural network and the learning rate are the same for GPOMDP and SVRPG.
In SVRPG we implemented two different Adam parameters: the first one for Snapshot and the second one for sub-iterations.
We use the stopping condition defined in Section \ref{sec:stopping}.
We fixed the maximum number of trajectories that both the algorithms can use.
